\documentclass[a4paper]{article}
\usepackage{fuzz}

\begin{document}

\section*{Scheduler}
\subsection*{Data types}
We have a given set $Proc$ of processes, each can be in one of
the states $idle$, $ready$ or $active$.
\begin{zed}
  [Proc]\\
  State ::= idle | readyd | active\\
\end{zed}

\subsection*{State}
The current global state consists of a set of processes and each process
has a assigned state. This is modelled as a partial function from the
set of all possible processes to their state. The current processes
are the domain of the function.

The system starts with no processes.
\begin{zed}
  Processes \defs [~proc: Proc \pfun State~]\\
  Init \defs [~Processes | proc = \emptyset~]\\
\end{zed}


\subsection*{Helper schemas}
The two following schemas are used by the operations defined
below. $ProcBase$ is for operations that modify the state and
have a process as input. $ProcOperation$ has the additional
constraint that the given process is an existing process in
the system.
\begin{zed}
  ProcBase \defs [~\Delta Processes; p? : Proc~]\\
  ProcOperation \defs [~ProcBase | p? \in \dom proc~]  
\end{zed}


\subsection*{Process creation and destruction}
A new process is created.
\begin{schema}{New}
  ProcBase\\
  \where
  p? \notin \dom proc\\
  proc' = proc \oplus \{p? \mapsto idle\}
\end{schema}

An idle process is destroyed.
\begin{schema}{Del}
  ProcOperation\\
  \where
  proc(p?) = idle\\
  proc' = \{p?\} \ndres proc
\end{schema}


\subsection*{Changing the state of a process}

An idle process signalises that it's ready to enter the critical section.
\begin{schema}{Ready}
  ProcOperation\\
  \where
  proc(p?) = idle\\
  proc' = proc \oplus \{ p? \mapsto ready \}
\end{schema}

A process that is ready enters the critical section and is then active.
The process can only become active if no other process is active.
\begin{schema}{Enter}
  ProcOperation\\
  \where
  proc(p?) = ready\\
  proc \rres \{ active \} = \emptyset\\
  proc' = proc \oplus \{ p? \mapsto active\}
\end{schema}

An active process leaves the critical section.
\begin{schema}{Leave}
  ProcOperation\\
  \where
  proc(p?) = active\\
  proc' = proc \oplus \{ p? \mapsto idle \}
\end{schema}

\end{document}
start_logging(1302529375491,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
version(1302529375491,1,3,2,beta10,'$Rev: 5042 $','$LastChangedDate: 2010-03-30 17:57:13 +0200 (Tue, 30 Mar 2010) $').
options(1302529375491,[set_pref('D:/FORMAIS/ProB_Win/ProB_Win/lib',uzzlib),log('D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex')],['D:/FORMAIS/ProB_Win/ProB_Win/lib',uzz,>>,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.fuzz']).
date(1302529375491,datime(2011,4,11,10,42,55)).
prob_halted_prematurely(1302529375491).
start_logging(1302529376479,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
version(1302529376479,1,3,2,beta10,'$Rev: 5042 $','$LastChangedDate: 2010-03-30 17:57:13 +0200 (Tue, 30 Mar 2010) $').
options(1302529376479,[set_pref('D:/FORMAIS/ProB_Win/ProB_Win/lib',uzzlib),log('D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex')],['D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex','D:/FORMAIS/ProB_Win/ProB_Win/probcli.exe','D:/FORMAIS/ProB_Win/ProB_Win/lib',uzz,>>,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.fuzz','D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.pl']).
date(1302529376479,datime(2011,4,11,10,42,56)).
loading(1302529376479,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
start_logging(1302529577009,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
version(1302529577009,1,3,2,beta10,'$Rev: 5042 $','$LastChangedDate: 2010-03-30 17:57:13 +0200 (Tue, 30 Mar 2010) $').
options(1302529577009,[set_pref('D:/FORMAIS/ProB_Win/ProB_Winlib',uzzlib),log('D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex')],['D:/FORMAIS/ProB_Win/ProB_Winlib',uzz,>>,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.fuzz']).
date(1302529577009,datime(2011,4,11,10,46,17)).
prob_halted_prematurely(1302529577009).
start_logging(1302529578040,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
version(1302529578040,1,3,2,beta10,'$Rev: 5042 $','$LastChangedDate: 2010-03-30 17:57:13 +0200 (Tue, 30 Mar 2010) $').
options(1302529578040,[set_pref('D:/FORMAIS/ProB_Win/ProB_Winlib',uzzlib),log('D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex')],['D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex','D:/FORMAIS/ProB_Win/ProB_Win/probcli.exe','D:/FORMAIS/ProB_Win/ProB_Winlib',uzz,>>,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.fuzz','D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex.pl']).
date(1302529578040,datime(2011,4,11,10,46,18)).
loading(1302529578040,'D:\\09-PROJETOS_NETBEANS\\JOKER\\ex_Z\\scheduler.tex').
